
%!TEX program = xelatex
\documentclass{academiccv}




\begin{document}\raggedright

% display name as the document title
\namefont{Wentao Zhu}

% contact info
\vspace{1em}
\begin{minipage}[t]{0.495\textwidth}
  Department of Computer Science \\
 Peking University\\
  Haidian, Beijing\\
  P.R.China 100871
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  Email: walterzhu@pku.edu.cn \\
  Website: www.walterzhu.com \\
  % Phone: (+86) 188 1021 9277
\end{minipage}
\vspace{0.5em}


\section*{Education}

\begin{tablist}

\item[2016.9 - 2020.6]  \tab B.S. Computer Science, School of EECS, Peking University
\item[2017.9 - 2020.6]  \tab B.S. Economics, National School of Development, Peking University

\end{tablist}


\section*{Research Projects}

\begin{tablist}

\item[2017.4 - 2017.11] 	\tab \textbf {Genetic Sequential Logic Circuit Programming} \textbf
				     \\ \tab \emph{Advisor: Prof. Qi Ouyang (School of Physics, PKU)}\emph
				     \\ \tab - Demonstrate a framework of programmable biological sequential circuits.
				     \\ \tab - Design fundamental module for genetic sequential logic (Bio Flip-flop). 
				     \\ \tab - Develop sequential circuits design automation algorithms.
				      \\ \tab - Won Best Information Processing Project Nominee in iGEM 2017
				     
				     				     
\item[2017.7 - 2017.9] 	\tab \textbf {Graph Based Keywords Extraction of Academic Papers} \textbf
				     \\ \tab \emph{Advisor: Prof. Junfeng Hu (Institute of Computational Linguistics, PKU)}\emph
				     \\ \tab - Introduce priori knowledge from domain ontology to keywords extraction.
				     \\ \tab - Construct weighted graph to evaluate the importance of candidate terms.
				     \\ \tab - Cluster the extracted keywords into topics based on semantic relevance.
				     
\end{tablist}


\section*{Experience}

\begin{tablist}

\item[2018.6 - 2018.8] 	\tab \textbf {Visiting Student, Stanford University} \textbf
					\\ \tab \emph{ International Honors Program. California, United States}\emph
				      \\ \tab - Recommended by Peking University.
				     \\ \tab - Fulfilled intensive study of computer science.


\item[2017.8 - 2017.9] 	\tab \textbf {Software Engineer Intern, World Wildlife Fund} \textbf
					\\ \tab \emph{Voluntary Work. Beijing, China}\emph
				      \\ \tab - Help arrange enterprise resource planning system.
				     \\ \tab - Support office automation development.
				   
				     				     
\item[2017.7 - 2017.8] 	\tab \textbf {Student, Data Science Immersion} \textbf
				     \\ \tab \emph{Instructor: John W. Emerson (Department of Statistics, Yale University)}\emph
				     \\ \tab - An intensive program on data analysis and statistical computing with R.
				     \\ \tab - Supported by MOE-Microsoft Key Laboratory of Statistics and Information	.		  

\item[2016.9 - 2016.9] 	\tab \textbf {Staff, Social Good Summit 2016} \textbf
				     \\ \tab \emph{Voluntary Work. Beijing, China}\emph
				     \\ \tab - Organize the section hosted by UNDP and Bill \& Melinda Gates Foundation.
				     \\ \tab - Interview the lecturers including Derek Shen, President of LinkedIn China.	  
\end{tablist}

\section*{Selected Courses}

\begin{tablist}

% \item[3.68/4.00] \tab  \emph{Introduction to Computing (A) (Honor Track)}\emph, PKU
\item[3.88/4.00] \tab  \emph{Introduction to Information Science and Technique}\emph, PKU
\item[3.88/4.00] \tab \emph{Introduction of Synthetic Biology}\emph, PKU
% \item[3.68/4.00] \tab  \emph{Practice of Programming in C++}\emph, PKU
\item[3.95/4.00] \tab \emph{American Economy}\emph, PKU
\item[3.73/4.00] \tab \emph{Algorithm Design and Analysis}\emph, PKU
\item[3.97/4.00] \tab  \emph{Leading Edge of Artificial Intelligence and Industry Trend}\emph, PKU
\item[3.85/4.00] \tab \emph{Computer Vision and Deep Learning}\emph, PKU
\item[4.30/4.00] \tab \emph{Introduction to Scientific Computing}\emph, Stanford MATH 114

\item[4.00/4.00] \tab \emph{Data Mining and Analysis}\emph, Stanford STATS 202

\item[4.30/4.00] \tab \emph{Introduction to High Performance Computing}\emph, Stanford ME 344

\end{tablist}


\section*{Awards}

\begin{tablist}
	\item[2017.11] \tab International Genetically Engineered Machine Competition, Gold Medal

	\item[2018.2] \tab COMAP's Interdisciplinary Contest in Modeling, Meritorious Winner (8\%)

	\item[2018.6] \tab Apple WWDC18 Scholarship

	\end{tablist}


\section*{Test Scores}

\begin{tablist}
	\item[2018.1] \tab TOEFL 110
	\item[2018.8] \tab IELTS 7.5
	\end{tablist}


\section*{Skills and Methods}

\subsection*{Programming}
\begin{itemize}
	\item C, C++, Python, MATLAB, R, Swift, HTML, Javascript, \TeX{}
\end{itemize}

\subsection*{Frameworks}
\begin{itemize}
	\item Tensorflow, Keras, PyTorch
\end{itemize}

\subsection*{Language}

\begin{itemize}
	\item  Mandarin Chinese (native), English (proficient), Cantonese(elementary), French(elementary)
\end{itemize}



% display today's date as Month Year after a vertical space below the end of the text
\begin{center}
\vspace{6em}
%\vfill
Updated \monthyeardate\today
\end{center}



\end{document}
